Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-18 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add text on precip validation

>>>>

For the most part, using a three day window of the day before, day of, and day after a tropical cyclone in assessing precipitation exposure seemed to capture the effects of the storm while excluding precipitation from other weather systems. However, for storms that have tracks that make a loop, such as Allison (2001), this three day window may not be adequate.
